Towards Transparency and Open Science

### 2023-01-13 manuscript.Rmd
fitpaper does not fit the included pdf

\includepdf[pages=-,fitpaper=true, offset=5mm 0mm,frame=false]{papers/workflow.pdf}

@@

\includepdf[pages=-,fitpaper=true, offset=5mm 0mm,frame=false]{papers/tutorial.pdf}

@@

\includepdf[pages=-,fitpaper=true, offset=5mm 0mm,frame=false]{papers/prereg.pdf}

>>>>

\includepdf[pages=-, offset=5mm 0mm,frame=false]{papers/workflow.pdf}

@@

\includepdf[pages=-, offset=5mm 0mm,frame=false]{papers/tutorial.pdf}

@@

\includepdf[pages=-, offset=5mm 0mm,frame=false]{papers/prereg.pdf}
